\documentclass[hidelinks, 11pt,letterpaper]{article}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[default]{opensans}
    \usepackage{titlesec}
    \usepackage{enumitem}
    \usepackage{multicol}
    \usepackage{hyperref}
    \usepackage{geometry}
    \usepackage{amssymb}
    \pagestyle{empty}
    \raggedright
    \usepackage{hyperref}
    
% set title so correct title displays for any filename
\hypersetup{
    pdfauthor={Yiyi Shen},
    pdftitle={Yiyi Shen Resume},
}
    
\hypersetup{
    colorlinks=false
}

% ATS parsing
\input{glyphtounicode}
\pdfgentounicode=1

% margins
\geometry{letterpaper, margin=0.5in}

% custom \large and \Huge font sizes
\makeatletter %only needed in preamble
\renewcommand\large{\@setfontsize\large{13pt}{18}}
\renewcommand\Huge{\@setfontsize\Huge{25pt}{18}}
\makeatother

% set size of the bullet for texlive 2021
\setlist[itemize,1]{label=\large$\bullet$}

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\titleformat{\section}{
  \vspace*{-13pt}\scshape\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

\newcommand{\resumeItemListStart}{
    \begin{itemize}[itemsep=1pt, parsep=0pt, topsep=0pt]
}

\newcommand{\resumeItemListEnd}{
    \end{itemize}
}

% suppress end of lines with comments (https://texfaq.org/FAQ-spinmacro)
\newcounter{datediff}
\newcommand{\yearsSince}[1]{%
    \setcounter{datediff}{\year}%
    \addtocounter{datediff}{-#1}%
    \thedatediff%
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%==== Profile ====%
\begin{center}
    {\Huge Yiyi Shen}
    
    \vspace{6pt}
    765-714-4606
    |
    Skye\_one@hotmail.com
    |
    \href{https://yiyishen.com/}{yiyishen.com}
    |
    \href{https://www.linkedin.com/in/shen488/}{linkedin.com/in/shen488}
\end{center}
\vspace{-7pt}

%==== Education ====%
\section{Education}

\textbf{Purdue University} \hfill \textit{Aug. 2019 -- May. 2023}

B.S. in Mathematics \hfill Dean's List + Semester Honors

% \textbf{Relevant coursework:} Data Structures/Algorithms, Computer Architecture, Programming in C, Competitive Programming II

% \vspace{2mm}

\section{Skills}

\textbf{Languages:}
Python,
R,
Java,
JavaScript,
HTML/CSS,
XML,
Matlab,
Swift

\textbf{Tools/Frameworks:} Git, Linux, JIRA, JUnit, SQL

\textbf{Software testing}: Manual, Agile, Waterfall, Automation, Performance, Usability

%==== Experience ====%
\section{Experience}

\textbf{Ningbo-Zhoushan Port (Group) Co., Ltd} \hfill Ningbo, China

Test Engineer Intern \hfill \textit{May. 2022 -- Aug. 2022}

\resumeItemListStart
	\item Developed and implemented test plans for an online shopping platform hosted on a Linux server.
	\item Performed manual and automated testing, including unit, integration, system, and regression testing. Documented and tracked bugs and issues in JIRA.
\resumeItemListEnd

\textbf{Zanhe (Shanghai) Industrial Development Co., Ltd} \hfill Shanghai, China

Test Engineer Intern \hfill \textit{May. 2021 -- Aug. 2021}

\resumeItemListStart
	\item Created and executed comprehensive test plans for an IoT system, resulting in identifying and resolving numerous software defects.
        \item Designed and executed automated regression tests for an intelligent classroom platform, resulting in a 40\% improvement in overall software quality.
\resumeItemListEnd

\textbf{Dawei Intelligent Technology Co., Ltd} \hfill Ningbo, China

Assistant of general manager \hfill \textit{May. 2020 -- Dec. 2020}

\resumeItemListStart
	\item Assisted in the planning and execution of projects, including setting timelines, allocating resources, and monitoring progress.
        \item Collaborated with cross-functional teams to ensure project success and timely delivery.
        \item Conducted data analysis and created reports, providing valuable insights and recommendations to the General Manager.
\resumeItemListEnd

%==== Personal Projects ====%
\section{Projects}

\textbf{PostMan Website} | \emph{JavaScript, HTML/CSS, React, Node, MongoDB} \hfill \textit{Sep. 2022 -- Dec. 2022}

\resumeItemListStart
    \item Designed and developed a task-based delivery web application using React for the front end, following the MVC pattern to ensure clean and maintainable code. 
    \item Implemented Firebase for user authentication and Socket.IO for real-time communication between users. \item Programmed over 10 RESTful APIs using Express.js, with data stored in MongoDB. 
    \item Embedded Google Map API for route tracking, address search, and auto-fill functionality, resulting in a seamless and user-friendly delivery management experience.
\resumeItemListEnd

\textbf{Boiler Math} | \emph{Python, Flask, Swift, XPath} \hfill \textit {Jan. 2022 -- May. 2022}

\resumeItemListStart
    \item Developed a Python program to parse the HTML of Purdue Math Department's website, extracting and scraping all past exam links to compile a comprehensive database of exams.
    \item Built RESTful APIs using Flask and stored discussions on Back4app, ensuring scalable and efficient data management. Deployed the APIs on a Linux server with Nginx, Gunicorn, and Supervisor, resulting in a high-performance and reliable API service.
    \item Designed the GUI of an iOS application using Swift Storyboard and conducted extensive testing with real phones to ensure a seamless and user-friendly experience.
\resumeItemListEnd

	
\end{document}